A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
explain

We looked at the top ten expressions passed to core and
package \eval calls. 
For package \eval calls, the ten most frequently evaluated expressions account
for 80\% of the calls. The most frequently occurring call is to the
\eval in \c{ggplot2::ggproto} which happens over 68\% of the times. The
remaining expressions occur with a frequency of less than 4\%. They originate
from \c{plyr}, \c{VGAM}, \c{magrittr}, \c{??}

The most frequent ten expressions to eval calls from core R contribute to
85.2\% of all \eval calls.
\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{c("auto", "shell", "radix")} & 1987105 & 29.3\%\\
    \c{c("auto", "shell", "quick", "radix")} & 1593169  & 23.5\%\\
    \c{local(\{info <- loadingNamespaceInfo(...} & 1008632 &       14.9\%\\
    \c{c("onLoad", "attach", "detach", "onUnload")}   & 470566 &      6.9\%\\
    \c{c("append", "prepend", "replace")} &              261587&       3.9\% \\
    \c{c("left", "right", "centre", "none")} & 162086     & 2.4\%\\
    \c{c("no", "ifany", "always")}   &                71580 &       1.1\%\\
    \c{c("pearson", "kendall", "spearman")}  & 72962 &      1.1\%\\
    \c{\<NULL\>}& 75330  &      1.1\% \\
    \c{\<Integer Vector\>}&                 66279&       1\%\\\hline
  \end{tabular}
  \caption{Top ten eval calls in Core}
  \label{A}
\end{table*}

The most frequent ten expressions to eval calls from CRAN packages contribute to
90\% of all \eval calls.
\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{\<Environment\>} &                                                                                                                           1091474   &  68.2\%\\
    \c{column[rows] <<- what} &                                                                                                         55677    &   3.5\%\\
    \c{function(value) freduce(value, `_function_list`)} &                                                                              37251   &    2.3\%\\
    \c{c("default", "default2012", "default2011" ...}&      20610      & 1.3\%\\
    \c{force(..1)}                                        &                                                                             20461     &  1.3\%\\
    \c{alist(`_spec`)}                                   &                                                                              18532    &   1.2\%\\
    \c{inner}                                           &                                                                               18530   &    1.2\%\\
    \c{slot(family, "fini")}                           &                                                                                 7288   &    0.5\%\\
    \c{\~fitted(.)}                                    &                                                                                  4733   &    0.3\%\\
    \c{function(.) purrr::keep(., is.function)}      &                                                                                   4344  &     0.3\%\\\hline
  \end{tabular}
  \caption{Top ten eval calls in CRAN}
  \label{A}
\end{table*}

>>>>

We looked at the top ten expressions passed to core and package \eval calls. The
most frequent ten expressions to eval calls from core R contribute to 85.2\% of
all \eval calls.
\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{c("auto", "shell", "radix")} & 1987105 & 29.3\%\\
    \c{c("auto", "shell", "quick", "radix")} & 1593169  & 23.5\%\\
    \c{\{info <- loadingNamespaceInfo(...} & 1008632 &       14.9\%\\
    \c{c("onLoad", "attach", "detach", "onUnload")}   & 470566 &      6.9\%\\
    \c{c("append", "prepend", "replace")} &              261587&       3.9\% \\
    \c{c("left", "right", "centre", "none")} & 162086     & 2.4\%\\
    \c{c("no", "ifany", "always")}   &                71580 &       1.1\%\\
    \c{c("pearson", "kendall", "spearman")}  & 72962 &      1.1\%\\
    \c{NULL}& 75330  &      1.1\% \\
    \c{Symbol}&                 66279&       1\%\\\hline
  \end{tabular}
  \caption{Top ten eval calls in Core}
  \label{A}
\end{table*}

The expression \c{\{info <- loadingNamespaceInfo(...} is added by core R
to a package directory during installation. To load the package, this code is
executed. It creates a namespace for the package, injects the package bindings,
and attaches the namespace to the program search path. The \c{NULL} comes from a
call to \c{substitute(subset)} in \c{stats::model.frame.default} function which
has a default value of \c{subset} as \c{NULL}. The \c{Symbol} arises from a
call to \c{as.name} in \c{base::str} function that returns a symbol that is
looked up by evaluating it in a specific environment. The remaining cases arise
from calls to \c{match.arg} which is used to look up the default choices for a
variable and match against the choice passed by the caller.

The most frequent ten expressions to eval calls from CRAN packages contribute to
90\% of all \eval calls.
\begin{table*}[tb]
  \centering
  \begin{tabular}{l|rr} \hline
    Expression & Eval Call & Eval Call \% \\\hline
    \c{\<Environment\>} &                                                          1091474  & 68.2\%\\
    \c{column[rows] <<- what} &                                                    55677    & 3.5\%\\
    \c{function(value) freduce(value, `_function_list`)} &                         37251    & 2.3\%\\
    \c{c("default", "default2012", "default2011" ...}&                             20610    & 1.3\%\\
    \c{force(..1)}                                        &                        20461    & 1.3\%\\
    \c{alist(`_spec`)}                                   &                         18532    & 1.2\%\\
    \c{inner}                                           &                          18530    & 1.2\%\\
    \c{slot(family, "fini")}                           &                           7288     & 0.5\%\\
    \c{\~fitted(.)}                                    &                           4733     & 0.3\%\\
    \c{function(.) purrr::keep(., is.function)}      &                             4344     & 0.3\%\\\hline
  \end{tabular}
  \caption{Top ten eval calls in CRAN}
  \label{A}
\end{table*}
The most frequently occurring call is to the
\eval in \c{ggplot2::ggproto} which happens over 68\% of the times. The
remaining expressions occur with a frequency of less than 4\%. They originate
from \c{plyr}, \c{VGAM}, \c{magrittr}, \c{??}
